### 2016-10-26 sec-conclusion.tex
Write a first-draft conclusion.

\section{Conclusion}
% summarize the main contributions of the paper; summarize the experimental
% results; argue again for our novelty; discuss future directions

>>>>

\section{Conclusion}
% summarize the main contributions of the paper; summarize the experimental
% results; argue again for our novelty; discuss future directions
We proposed a two-layer hidden Markov model for MOOC student behavior
modeling in an unsupervised learning framework on large collections of
actions extracted from MOOC log data. This model is different from existing
methods in that it treats behavior patterns as a sequence of \emph{latent
states}, rather than assigning these states in a rule-based manner. It
allows for students to exhibit different behaviors over time, and allows
analysis at different levels of granularity.

We showed that such a model does in fact capture meaningful behavior
patterns and produces descriptions of these behavior patterns that are easy
to interpret. We argued that it is important to capture student behavior
patterns with more sophisticated models than simple discrete distributions
over actions in order to capture information present in bigrams of actions
(or above). By varying the parameter $K$ controlling the number of latent
states inferred, we showed that the model is flexible and can capture
patterns of differing levels of specificity in this way.  Finally, we
investigated whether we can detect differences in student behavior patterns
as they correlate with course performance. Specifically, we demonstrated
that high-performing students produce substantially different HMM
transition diagrams.

\subsection{Future Work}

Our model can be used to produce an ordered list of latent states for each
student over time. Given these labeled sequences, we could correlate
course-wide drifts in these latent states with events in a course. For
example, we might be able to automatically discover difficult or confusing
parts of a course by noticing spikes in the distribution of students over
latent states over time.

Our model does not explicitly model drop-out like
\citet{Kizilcec:2013:LAK}, but doing so is an obvious extension. Our model
should be able to provide predictions of when a student is ``at risk'' for
dropping out under such an extension.

Currently, the model learns a transition matrix over the latent states that
is \emph{shared} across all students. It would be interesting to instead
learn a different latent state transition matrix for each individual
student, but keep the second-level Markov models shared. This would provide
the model with more flexibility which may be desirable itself, but would
also naturally result in a description of a student (via his or her HMM
transitions) that could be incorporated into existing supervised learning
techniques that try to predict student outcomes.
